The Shape and Color of Politics

### 2023-10-18 chapter_2/src/roberts_empirical_chapter_1.qmd
adding the summary stats of the measure for proportion of colors on yard signs

Next, I use a combination of HTML and XML tags to identify then download around 1,000 yard signs from House elections from the years 2016 to 2024 from the website provided by the Center for American Politics and Design. I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.

@@

I then extract the non-black pixels from my array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$]

>>>>

Next, I use a combination of HTML and XML tags to identify then download around 1,000 yard signs from House elections from the years 2016 to 2022 from the website provided by the Center for American Politics and Design. I used the `OpenCV` library in `Python` to examine the proportion of the colors near the "Republican red"^[lower RGB values: 93, 9, 12; upper RGB values: 236, 69, 75] and "Democratic blue"^[lower RGB values: 0, 18, 26; upper RGB values [102, 212, 255]] in each of these yard signs.

@@

I then extract the non-black pixels from my array and calculate the percentage of pixels in the image that are not black.^[$\text{Color} \% = \frac{\text{Non-black}}{\text{Transformed}} \times \frac{\text{Original}_{\text{Height}} + \text{Original}_{\text{Width}}}{2\text{Transformed}_{\text{Height}} + 2\text{Transformed}_{\text{Width}}}$] Summary statistics of these calculated proportions for red and blue are included in the [Appendix](#tbl-yard-sign-summary).

### 2023-10-18 chapter_2/src/slides/slides.qmd
adding the summary stats of the measure for proportion of colors on yard signs

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: false
    slide-number: true
    toc: false
    #toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/candidate_support_chapter_references.bib   
    self-contained: true
    output-file: color-book.html
execute:
  echo: false
  freeze: true
nocite: |
  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
---

@@

# Load cleaned data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../../data/clean/cleaned_pavlovia.csv"
)
# Load fitted models
  #* Pre-test
load(
    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
  )
  #* Main studies
load("../../data/temp/models/study_1_fitted.RData")
```

@@

@@

![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}

@@

### Outcome variable - How much red and blue do campaigns use?

@@

### Predictor variable - What is the partisan composition of the district?

@@

### Do campaigns use a different proportion of the colors red and blue based on partisan composition?

@@

::: {.r-stack #fig-trial-1}

![Red condition](../study_1/assets/rep_yard_sign_round_1.png){.fragment #fig-red-1 width="6.5in"}

![Blue condition](../study_1/assets/dem_yard_sign_round_1.png){.fragment #fig-blue-1 width="6.5in"}

![White condition](../study_1/assets/cont_yard_sign_round_1.png){.fragment #fig-white-1 width="6.5in"}

Trial 1
:::

@@

::: {.r-stack #fig-trial-2}

![Red condition](../study_1/assets/rep_yard_sign_round_2.png){.fragment #fig-red-2 width=6.5in}

![Blue condition](../study_1/assets/dem_yard_sign_round_2.png){.fragment #fig-blue-2 width=6.5in}

![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-2 width=6.5in}

Trial 2
:::

@@

::: {.stack #fig-trial-3}

![Red condition](../study_1/assets/rep_yard_sign_round_3.png){.fragment #fig-red-3 width=6.5in}

![Blue condition](../study_1/assets/dem_yard_sign_round_3.png){.fragment #fig-blue-3 width=6.5in}

![White condition](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment #fig-white-3 width=6.5in}

Trial 3
:::

>>>>

---
title: "The Shape and Color of Politics"
author:
  - name: Damon C. Roberts [{{< fa brands orcid size=xs >}}](https://orcid.org/0000-0002-4360-3675)
format:
  revealjs:
    multiplex: true
    embed-resources: true
    theme: [dark, ../../assets/slides/custom.scss]
    transition: slide
    scrollable: true
    incremental: false
    slide-number: false
    progress: false
    menu: false
    toc: false
    #toc-depth: 2
    slide-level: 5
    bibliography: ../../../assets/candidate_support_chapter_references.bib   
    self-contained: true
    output-file: color-book.html
    fig-responsive: false
    margin: 0.1
execute:
  echo: false
  freeze: true
  eval: true
  cache: true
nocite: |
  @allaire_quarto_2022, @arel-bundock_marginaleffects_2022, @wickham_ggplot2_2016, @leeuw_jspsych_2015, @burkner_brms_2017,
---

@@

# Load cleaned data
list_df <- list()
list_df[["cleaned"]] <- read.csv(
  file = "../../data/clean/cleaned_pavlovia.csv"
)
# Load fitted models
  #* Pre-test
load(
    file="../../data/models/prr/pre-test/pre-test_party_model.RDS"
  )
  #* Main studies
load("../../data/temp/models/study_1_fitted.RData")
# Load data for study 2
df_study_2 <- read.csv("../../data/clean/study_2.csv") |>
  as.data.table()
  #* convert state_district and year variables  to factors
df_study_2 <- df_study_2[
  , year := tstrsplit(year, "-", keep = 1)
][
  , year := as.numeric(year)
][
  , state_district := factor(state_district)
][
  , blue_prop := blue_percent / 100
][
  , red_prop := red_percent / 100
]
```

@@

![[Shell]()](../../assets/slides/imgs/shell.png){#fig-shell width=6.5in}

```{mermaid}
%%| label: fig-shell-color
%%| fig-cap: Associative memory
%%| eval: true
flowchart LR;

A["Yellow"]
A --> B["Banana"]
A --> C["Rubber duck"]
A --> D["Shell"]
A --> E["Leaves"]
```

```{mermaid}
%%| label: fig-shell-affect
%%| fig-cap: Object evaluation
%%| eval: true
flowchart LR;

A["Yellow"]
A -.-> B["Banana"]
A -.-> C["Rubber duck"]
A --> D["Shell"]
A -.-> E["Leaves"]
D --> F["Avoid"]
```

<!--
---

@@

-->
![[Example of brand UI]()](../../assets/slides/imgs/green_bubble.jpeg){.absolute left=100 width=4.5in #fig-brand-ui}
![[The great divide]()](../../assets/slides/imgs/green_bubble_funny.png){.absolute right=100 width=4.5in #fig-brand-divide}

@@

### Measurement: How much red and blue do campaigns use?

@@

```{r}
#| label: tbl-yard-sign-summary
#| tbl-cap: Summary statistics
names(df_study_2)[names(df_study_2) == 'red_percent'] <- '% Red'
names(df_study_2)[names(df_study_2) == 'blue_percent'] <- '% Blue'
names(df_study_2)[names(df_study_2) == 'white_percent'] <- '% White'

df_study_2_subset <- df_study_2[, c('% Red', '% Blue', '% White')]
datasummary_skim(
  df_study_2_subset
  , notes = "Data source: CAPD Yard Signs."
  , histogram = FALSE
)

### Measurement: What is the partisan composition of the district?

@@

### Do campaigns use a different proportion of the colors red and blue in different constituency compositions?

@@

::: {.r-stack}

![](../study_1/assets/rep_yard_sign_round_1.png){.fragment width="6.5in"}

![](../study_1/assets/dem_yard_sign_round_1.png){.fragment width="6.5in"}

![](../study_1/assets/cont_yard_sign_round_1.png){.fragment width="6.5in"}

:::

@@

::: {.r-stack}

![](../study_1/assets/rep_yard_sign_round_2.png){.fragment width=6.5in}

![](../study_1/assets/dem_yard_sign_round_2.png){.fragment width=6.5in}

![](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment width=6.5in}

:::

@@

::: {.r-stack}

![](../study_1/assets/rep_yard_sign_round_3.png){.fragment width=6.5in}

![](../study_1/assets/dem_yard_sign_round_3.png){.fragment width=6.5in}

![](../study_1/assets/cont_yard_sign_round_2_3.png){.fragment width=6.5in}

:::
